\documentclass[10pt,a4paper,oneside]{article}

\input{proposal_config}


\title{Example Title}
\author{Author Name}
\date{Planned Registration Date}
\advisor{M.Sc. Your Advisor}
\supervisor{Prof. Dr. Thomas Thüm}
\thesistype{Bachelor} %Master


\begin{document}
	\maketitle

	\section{Introduction}
	In one to two pages, the introduction motivates the research topic and gives an overview over the related scientific work using citations~\cite{TBK:ICSE09}.
	The introduction starts with the significance of the  general research area and then leads reader attention step-wise to the area of the specific research problem of the thesis.
	That means that the introduction is structured like an inverted triangle, starting with the general research area and then focusing more and more on the specific context of the thesis.

	$\Rightarrow$ Why is your research important?
	
	\section{Problem Statement}
	In three to four sentences, the problem statement describes the research problem the thesis aims to address.

	$\Rightarrow$ What problem does your research plan to solve?

	\section{Contribution}
	In three to four sentences, the contributions section lists the planned scientific contributions of your work.
	This naturally includes the findings of your research, but can also include reusable data sets, newly created tools, \dots

	$\Rightarrow$ How do you plan to address your research problem?

	\subsection{Work Packages}
	
	\begin{enumerate}
		\item \textbf{WP1 -- First Work Package Headline}\\
			For each work package, you give a description of one to two sentences.
		\item \textbf{WP2 -- Second Work Package Headline}\\
			This helps you to structure the necessary steps to achieve your research goal.
	\end{enumerate}

	\subsection{Schedule}
	% FOR BACHELOR'S THESIS
	\begin{center}
		\begin{ganttchart}[hgrid, vgrid,expand chart=\textwidth, milestone/.append style={fill=primary, rounded corners=3pt}]{1}{12}
			\gantttitle{Week}{12} \\
			\gantttitlelist{1,...,12}{1} \\
			\ganttbar{WP1}{1}{4} \\
			\ganttmilestone{Intermediate presentation}{4} \\
			\ganttbar{WP2}{5}{9} \\
			\ganttbar{WP3}{7}{11} \\
			\ganttbar{Buffer}{12}{12} \\
			\ganttmilestone{Final presentation}{12}
		\end{ganttchart}
	\end{center}

	% FOR MASTER'S THESIS
%	\begin{center}
%		\begin{ganttchart}[hgrid, vgrid,expand chart=\textwidth, milestone/.append style={fill=primary, rounded corners=3pt}]{1}{24}
%			\gantttitle{Week}{24} \\
%			\gantttitlelist{1,...,24}{1} \\
%			\ganttbar{WP1}{1}{4} \\
%			\ganttmilestone{Intermediate presentation}{6} \\
%			\ganttbar{WP2}{5}{9} \\
%			\ganttbar{WP3}{7}{11} \\
%			\ganttbar{WP4}{11}{23} \\
%			\ganttbar{Buffer}{24}{24} \\
%			\ganttmilestone{Final presentation}{24}
%		\end{ganttchart}
%	\end{center}

	% Literature
	\printbibliography
\end{document}